Semantic information inside sentence embeddings

### 2023-05-11 paper/paper.tex
Add hints how to restructure the paper.

@@

% Deep dive into the properties of the datsaet
%   - transformation terminology
%   - types and explanations of transformations
%   - dataset statistics (count of seeds, sentences in total, transformation
%   distributions)

@@

\section{Methodology of Embedding Evaluation}

@@

@@

@@

@@

Lastly, we employ several supervised approaches to classify the embeddings and evaluate the extent to which the derivation classes can be captured by the trained classifiers. The accuracy scores are compared among classifiers including Multilayer Perceptron, Decision tree and Support Vector Machine.

@@

>>>>

Transformation \Trans{future} ....

@@

% Deep dive into the properties of the datsaet
%   - transformation terminology = transformation
%   - contextualized and distance vector to relation vector
%   - types and explanations of transformations
%   - dataset statistics (count of seeds, sentences in total, transformation
%   distributions)

We define \emph{relation vector} as the ....

@@

@@

\subsubsection{Visualization}

\subsubsection{Cosine similarity}

@@

\subsubsection{CHI index}

@@

\subsubsection{GM}

@@

% Lastly, we employ several supervised approaches to classify the embeddings and
% evaluate the extent to which the derivation classes can be captured by the
% trained classifiers. The accuracy scores are compared among classifiers
% including Multilayer Perceptron, Decision tree and Support Vector Machine.

@@

\section{Conclusion}

% Summarize our results. Put them to context?
